---
title: "Analysis of Mousetracking Data"
author: "Laura Paulsen"
date: "3/15/2022"
output: html_document
---

## To-do/questions
* Should we remove neutral battery? Really difficult to see
* Calculate velocity and acceleration - DONE BUT NOT SURE HOW TO EXTRACT VALUES


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, mousetrap)
```

```{r}
filepath = 'Stroop_mouse_EEG_data/behavioural/participant_a_13_54_30.csv'
```

### Reading in data and filtering 
```{r}
data_loaded <- read_csv(filepath)
data_filtered <- data_loaded %>% filter(phase == 'experimental') %>% filter(accuracy == 1)
data_filtered$trial_number <- as.factor(data_filtered$trial_number)
```


### Count numbers of incorrect trials
```{r}

```


### Making the data compatible with the mousetracking package (note: not needed with newest version of experimental script)
This is done by instead of having a row for each mouse measurement we have a row for each trial. Then the xpos, ypos and timestamp variables are shown as a list of measurements. 
```{r}
df <- tibble()

for(i in 1:length(unique(data_filtered$trial_number))){
  data <- data_filtered %>% filter(trial_number == i)
  
  ypos <- list(data$ypos)
  xpos <- list(data$xpos)
  trial_timestamps <- list(data$trial_timestamp)
  

  newDat <- tibble(ID = data$ID[1], 'rt' = data$rt[1], 'left_img' = data$left_img[1], 'right_img' = data$right_img[1], "trial_number" = data$trial_number[1], 'trial_type' = data$trial_type[1], "correct_resp" = data$correct_resp, 'xpos' = xpos, 'ypos' = ypos, 'trial_timestamps' = trial_timestamps)
  
  df <- rbind(df, newDat)
}
```


### Creating a mousetrap object
```{r}
mouse <- mt_import_mousetrap(df, xpos_label = 'xpos', ypos_label = 'ypos', timestamps_label = 'trial_timestamp')
```


### Derivatives
```{r}
mouse <- mt_derivatives(mouse)
```


### First plots
```{r}
mt_plot(mouse)
```

#### Colouring by trial type
```{r}
mt_plot(mouse, color ="trial_type")
```

#### Mirror-symmetric mapping of all the movements from the right side to the left side so that all movements overlap
```{r}
mouseremap <- mt_remap_symmetric(mouse)
mt_plot(mouseremap, color ="trial_type")
```

#### Plotting x pos against time stamps
```{r}
mt_plot(mouseremap, x = 'timestamps', y = 'xpos')
```

#### Removing finish and initiation
```{r}
#nofinish <- mt_exclude_finish(mouseremap)
noinitiation <- mt_exclude_initiation(mouseremap)
mt_plot(noinitiation, x = 'timestamps', y = 'xpos')
```


### Aligning start and end point
```{r}
aligned <- mt_align_start_end(noinitiation)
mt_plot(aligned)
```



### Normalizing time and then plotting again
```{r}
mousetime <- mt_time_normalize(aligned)
```

```{r}
mt_plot(mousetime, use = 'tn_trajectories') #tn_trajectories are time normalized
```

#### Plotting averages
```{r}
mt_plot_aggregate(mousetime, use = 'tn_trajectories', color = 'trial_type') # time normalized
mt_plot_aggregate(mousetime, use = 'trajectories', color = 'trial_type') # normal


```

